\textbf{EECS 340: Assignment 7}

### 2020-04-28 assignment_7/article.tex
🔨 Add comments to P1(a) pseudocode.

\begin{algorithm}[H]
\caption{DFS(G)}
    \begin{algorithmic}[1]
        \Procedure{DFS}{G}
        \For{each $u \in G.V$}:
            \State $u.color$ = WHITE
            \State $u.z = NULL$
        \EndFor
        \For{each $u \in G.V$}:
            \If{$u.color$ == WHITE}
                \State \textsc{DFS-Game-Visit(G, u)}
            \EndIf
        \EndFor
        \For{each $u \in G.V$}:
            \State print $u.team, u.z$
        \EndFor
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{DFS-Game-Visit(G, u)}
    \begin{algorithmic}[1]
        \Procedure{DFS-Game-Visit}{G, u}
        \State $z = NULL$
        \State $u.color$ = GRAY
        \For{each $v \in Adj(u)$}:
            \If{$v.color$ == WHITE}
                \State $z = v.rank$
                \State $z = \min(z, \textsc{DFS-Game-Visit(G, v)})$
            \Else
                \State $z = \min(z, v.z)$
            \EndIf
        \EndFor
        \State $u.color$ = BLACK
        \If{$z == NULL$}
            \State $u.z = \infty$
            \State $z = u.rank$
        \Else
            \If{$u.z == NULL$}
                \State $u.z = z$
            \Else
                \State $u.z = \min(u.z, z)$
            \EndIf
        \EndIf
        \State \Return $z$
    \end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}[H]
\caption{DFS-Game-Visit(G, u)}
    \begin{algorithmic}[1]
        \Procedure{DFS-Game-Visit}{G, u}
        \State $z = NULL$ \Comment{Potential $z$ value for this node, if not end of tree.}
        \State $u.color$ = GRAY
        \For{each $v \in Adj(u)$}:
            \If{$v.color$ == WHITE}
                \State $z = v.rank$ \Comment{If have decendent, set decedent's $rank$ as current's $z$.}
                \State $z = \min(z, \textsc{DFS-Game-Visit(G, v)})$ \Comment{Find the lowest $z$ from all decendents.}
            \Else
                \State $z = \min(z, v.z)$ \Comment{Check if explored reachable nodes have lower $z$.}
            \EndIf
        \EndFor
        \State $u.color$ = BLACK
        \If{$z == NULL$} \Comment{If this node is end of tree.}
            \State $u.z = \infty$ \Comment{Set $z$ to $\infty$ to indicate beats no one.}
            \State $z = u.rank$ \Comment{For ancestor nodes to read its rank during recursion.}
        \Else
            \If{$u.z == NULL$}
                \State $u.z = z$
            \Else
                \State $u.z = \min(u.z, z)$ \Comment{If node have been explored, check if the tree's $z$ is better.}
            \EndIf
        \EndIf
        \State \Return $z$
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{DFS(G)}
    \begin{algorithmic}[1]
        \Procedure{DFS}{G}
        \For{each $u \in G.V$}:
            \State $u.color$ = WHITE
            \State $u.z = NULL$
        \EndFor
        \For{each $u \in G.V$}:
            \If{$u.color$ == WHITE}
                \State \textsc{DFS-Game-Visit(G, u)}
            \EndIf
        \EndFor
        \For{each $u \in G.V$}:
            \State print $u.team, u.z$ \Comment{output all $z_i$.}
        \EndFor
    \end{algorithmic}
\end{algorithm}
